InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
changed determine to evaluate
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>
Abstract (#59)
* abstract draft

* changed determine to evaluate

Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

---------

Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content. This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g. to detect fake news. This arises the field of tricking AI content detectors to create unrecognized AI generated content to bypass the mentioned AI detectors on the one hand and on the other hand this field is sufficient to improve the existing AI content detectors for more reliability and stability. The following paper tries to evaluate some methods to fool different AI detectors on differently generated images and texts.
\end{abstract}
